Data_visualization

### 2018-08-07 Rmd/Data_visualization.Rmd
caan csv processed file

#There are 3 crosses were seeds were lost (2,7,9)
#load libraries
library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)
#read data and cleaning
pein_seed_set_final <- read.csv("Data/pein_seed_set_final.csv")
pein_seed_set_final=pein_seed_set_final[,-1]

cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
#Colur per family

@@

library(stringr)
caan_seed_set_div <- str_split_fixed(as.character(caan_seed_set$Treatment), " ", 2)
caan_seed_set_div <- data.frame(caan_seed_set_div, stringsAsFactors = F)
colnames(caan_seed_set_div)=c("non_focal","percentage")
caan_seed_set_bind <- cbind(caan_seed_set,caan_seed_set_div)
caan_seed_set_bind <- filter(caan_seed_set_bind, percentage!="100%")

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(caan_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

caan_seed_set_cross <- filter(caan_seed_set_bind, non_focal %in% c("CROSS"))
caan_seed_set_self <- filter(caan_seed_set_bind, non_focal %in% c("SELF"))
caan_seed_set_control <- filter(caan_seed_set_bind, non_focal %in% c("CONTROL"))
caan_seed_set_flower <- filter(caan_seed_set_bind, non_focal %in% c("FLOWER"))

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CROSS"),]
caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("SELF"),]
caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CONTROL"),]
caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("FLOWER"),]

caan_seed_set_final<-rbind(caan_seed_set_bind,caan_seed_set_cross, caan_seed_set_self, caan_seed_set_control,
                           caan_seed_set_flower)
#deleting extra columns used for data formating
caan_seed_set_final=caan_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
caan_seed_set_final[caan_seed_set_final$Treatment==c("CAAN 50%"),4] <- NA

#changing non_focal species name
caan_seed_set_final$Treatment=as.character(caan_seed_set_final$Treatment)
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CROSS"] <- "Cross"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SELF"] <- "Self"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CONTROL"] <- "Control"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"

caan_seed_set_brassicaceae <- filter(caan_seed_set_final, Family %in% c("Brassicaceae"))
caan_seed_set_convolvulaceae <- filter(caan_seed_set_final, Family %in% c("Convolvulaceae"))
caan_seed_set_solanaceae <- filter(caan_seed_set_final, Family %in% c("Solanaceae"))
caan_seed_set_final$Family[is.na(caan_seed_set_final$Family)] <- "Solanum lycopersicum"
caan_seed_set_cross=caan_seed_set_cross[,-c(5,6)]
caan_seed_set_cross$Family <- "other"
caan_seed_set_self=caan_seed_set_self[,-c(5,6)]
caan_seed_set_self$Family <- "other"
caan_seed_set_control=caan_seed_set_control[,-c(5,6)]
caan_seed_set_control$Family <- "other"
caan_seed_set_flower=caan_seed_set_flower[,-c(5,6)]
caan_seed_set_flower$Family <- "other"

caan_seed_set_final=rbind(caan_seed_set_brassicaceae, caan_seed_set_convolvulaceae, 
                          caan_seed_set_solanaceae, caan_seed_set_cross, caan_seed_set_self, caan_seed_set_control,
                          caan_seed_set_flower)

cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
#Colur per family
#Different colour per family
b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

>>>>

#There are 3 crosses were seeds were lost (2,7,9)
#load libraries
library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)
#read data and cleaning
pein_seed_set_final <- read.csv("Data/pein_seed_set_final.csv")
pein_seed_set_final=pein_seed_set_final[,-1]
#load the palette for all the 4 plots
cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
#Colur per family

@@

#
##
###
#C. ANNUUM 
###
##
#
caan_seed_set_final <- read.csv("Data/caan_seed_set_final.csv")
caan_seed_set_final=caan_seed_set_final[,-1]

#Colur per family
#Different colour per family
b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
